---
title: "Sim HW5"
author: "Bridget McGowan"
date: "11/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(foreach)
library(doParallel)
library(parallel)
```


# Question 1 


(25 points) Write a function that returns a randomly chosen letter of the alphabet.
```{r cars}
alph<-function(x){
  sample(letters,1)
}

```
# Question 2

(25 points) Run this function some large number of times (e.g. 100000 or 1000000) using parallel computation. Compare the time it takes to running it not in parallel.\  



```{r}

set.seed(1)
start<-Sys.time()
lapply_test<-lapply(1:1000000,alph)
stop<-Sys.time()
stop-start


cores<-detectCores()-1

start<-Sys.time()
cl<-makeCluster(cores)

par_test<-parLapply(cl,1:1000000,alph)
stop<-Sys.time()
stop-start



start<-Sys.time()
mc_test<-mclapply(1:1000000,alph)
end<-Sys.time()
end-start
```

#Question 3 and 4 

(25 points) Create an R package that contains this function.\ 

(25 points) If you do not have one, set up a github account. Put the
package on github.\  

www.github.com/bridgetmcgowan/SImulation_HW5 \  

Test 
```{r}
# library(devtools)
# install_github("bridgetmcgowan/SImulation_HW5",force=T)
# library(returnALetter)
# alph(1)
```

